\documentclass{scrreprt} 
\usepackage[utf8]{inputenc} 
\usepackage{lmodern} 
\usepackage[ngerman]{babel}% Das Paket ngerman ist veraltet! 
\usepackage{blindtext} 

\title{Interactive Visual Computing \\ Animation movie project:}
\subtitle{\huge{Matrix - Rayloaded}}
\author{Dennis Sobczak \\ Marvin Somma \\ Sebastian Graba \\ Kim Daertz}

\begin{document} 
\maketitle
%\blinddocument 
\textbf{Story}:

\noindent In the beginning of our movie the animated \emph{Matrix - Rayloaded} movie title appears in the front of a dark background. The image then flashes (white) and dissolves into another scene where a chessboard like ground appears to the spectator (look from top at the ground). The camera then rotates and goes down to the ground, scrolling towards a humanoid, Neo. The scene flashes again and Neo appears on a beach (Pirates of the Carribbean). Suddenly native people run towards him, carrying spears. Neo turns around and runs away. Then on a palm tree he discovers a red telephone ringing. He takes the phone and disappears (white flash) into another scene, where he lies on the ground, awakening. He looks at agent Smith, who koed him before. He stands up and the scene turns slowly black, showing Neo stepping towards Smith. END \\

\textbf{Figures}:
\begin{itemize}
\item{The Matrix movie protagonist \emph{Neo} (Keanu Reeves)}
\item{The Matrix movie protagonist \emph{Agent Smith}}
\item{Native people from the Pirates of the Carribbean 2 movie}
\item{The telephone cell palm tree}
\end{itemize}

\end{document}
